---
title: "Data Import"
author: "Ali Early"
output: github_document
---

This file is for doing data import.

````{r}
library(tidyverse)
````

```{r}
litters_df =
  read_csv(file = "data/FAS_litters.csv")

litters_df = janitor::clean_names(litters_df)
```


```{r}
pups_df =
  read_csv(file = "data/FAS_pups.csv", skip = 3)

litters_df = janitor::clean_names(pups_df)
```

names(litters_df)

litters_df = janitor::clean_names(litters_df)

names(litters_df)

view(pups_df)

pups_df = 
    read_csv(file = "./data/FAS_pups.csv", skip = 3)

pups_df = 
    read_csv(
        file = "data/FAS_litters.csv",
        skip = 3)
        
litters_df

tail(litters_df, 5)

skimr::skim(litters_df)

view(litters_df)

litters_df = 
    read_csv(file = "./data/FAS_litters.csv",
    skip = 10, col_names = FALSE)
    
head(litters_df)

litters_df = 
    read_csv(
        file = "./data/FAS_litters.csv",
        na = c(".", "NA", ""))
        
head(litters_df)

litters_df = 
    read_csv(file = "./data/FAS_litters.csv",
        na = c(".", "NA", ""),
    col_types = cols(
      Group = col_character(),
      `Litter Number` = col_character(),
      `GD0 weight` = col_double(),
      `GD18 weight` = col_double(),
      `GD of Birth` = col_integer(),
      `Pups born alive` = col_integer(),
      `Pups dead @ birth` = col_integer(),
      `Pups survive` = col_integer()
    )
  )
  
tail(litters_df)

litters_df = 
    read_csv(file = "./data/FAS_litters.csv",
        na = c(".", "NA", ""),
    col_types = cols(
      Group = col_factor()
    )
)

head(litters_df)

pups_df = 
    read_csv(
        file = "./data/FAS_pups.csv",
        skip = 3,
        na = c(".", "NA"), col_types = "fddddd")

skimr::skim(pups_df)


## Look at the data

```{r}
litters_df
pups_df
```